---
title: "Lab4"
author: "Simon Jonsson, Fanny Karelius"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
library(lab4)
data(iris)
```
This lab is for the purpose of implementing some of the simple features of the **lm** class. Methods will be declared below

## General information
Package implements linear regression models, called **linreg** and is called as an example:
```{r, results = "hide"}
ex_form <- Petal.Length ~ Sepal.Width + Sepal.Length
linreg_ex <- linreg$new(formula=ex_form, data=iris)
```

The package calculates the following formulas:
**Regression coefficients:**
$$\mathbf{\hat{\beta} = \left(X^\intercal X\right)^{-1} X^\intercal y}$$
**The fitted values:**
$$\mathbf{\hat{y} = X \hat{\mathrm{\beta}}}$$
**The residuals:**
$$\mathbf{\hat{e} = y - \hat{{y}} = y - X \hat{\mathrm{\beta}}}$$
**The degrees of freedom:** where $n$ is the number of observations and $p$ is the number of parameters in the model.
$$df=n-p$$

**The residual variance:**
$$\hat{\sigma}^2 = \mathbf{\frac{e^\intercal e}{df}}$$
**The variance of the regression coefficients:**
$$\mathbf{\mathrm{Var} \left( \hat{\mathrm{\beta}} \right)} = \hat{\sigma}^2 \mathbf{(X^\intercal X)^{-1}}$$
**The t-values for each coefficient:**
$$ t_\beta = \frac{\hat{\beta}}{\sqrt{\mathrm{Var} \left( \hat{\beta} \right)}}$$

## Methods

Implemented methods are as follows:

**print()** prints out the coefficients and coefficient names, similar as done by the lm class
```{r}
linreg_ex$print()
```

**plot()** returns **Scale-Location** and **Residuals vs Fitted** plots p1 and p2 respectively
```{r}
linreg_ex$plot()
```

**resid()** returns a vector of residuals $\mathbf{\hat{e}}$
```{r}
linreg_ex$resid()
```

**pred()** returns the predicted values $\mathbf{\hat{y}}$ 
```{r}
linreg_ex$pred()
```

**coef()** returns the coefficients as a **named** vector
```{r}
linreg_ex$coef()
```

**summary()** prints out the coefficients with their **standard error**, **t-value**, and **p-value** as well as the estimate of $\hat{\sigma}$ and the degrees of freedom in the model

```{r}
linreg_ex$summary()
```
